# Contents {#contents}

```{r}
#| echo: false
source("glossary_setup.R")
```

The `r glossary("pipeline")` provides a set of handy tools listed below, which I will also go through:

-   `r glossary("Bash")` pipeline to process multiple subject folders to do cropping, bias correction and skull stripping before registering brain and possibly lesion mask to 1 or 2 mm `r glossary("MNI")` space (this is the primary content). The `r glossary("registration")` can be performed with `r glossary("fsl")` or `r glossary("ANTs")`.

-   A few other `r glossary("Bash")`-scripts to register brain and lesion mask after manual correction of brain mask (no, even using `r glossary("optiBET")` is not perfect), and to do other things.

-   A few *`r glossary("R")`*-scripts to organise files and to package lesion masks to supply to the `r glossary("NeMo")` tool in @sec-nemo.

-   In a separate folder (`nemo/`) I've included a few scripts to collect data from the `r glossary("NeMo")`-output and do basic visualisation based on the `r glossary("NeMo")` output data.

-   Finally, three `r glossary("Python")` scripts from the `r glossary("NeMo")`-[repository](https://github.com/kjamison/nemo): `nemo_save_average_glassbrain.py`, `nemo_save_average_graphbrain.py` and `nemo_save_average_matrix_figure.py`. These are used for data visualisation in the included pipeline use case example in @sec-nemo. The NeMo-project project, however is shared without a license. The files can be downloaded from the [NeMo-repository](https://github.com/kjamison/nemo) or directly with the following lines of code:

    ```{r}
    #| eval: false
    download.file("https://raw.githubusercontent.com/kjamison/nemo/master/nemo_save_average_glassbrain.py", here::here("nemo_save_average_glassbrain.py"))
    download.file("https://raw.githubusercontent.com/kjamison/nemo/master/nemo_save_average_graphbrain.py", here::here("nemo_save_average_graphbrain.py"))
    download.file("https://raw.githubusercontent.com/kjamison/nemo/master/nemo_save_average_matrix_figure.py", here::here("nemo_save_average_matrix_figure.py"))
    ```

## Glossary

```{r}
#| echo: false
glossary::glossary_table()
```
