# Using the NeMo tool {#nemo}

```{r}
source("glossary_setup.R")
```

This section will exists as documentation on how we have worked with the `r glossary("NeMo")` tool. Coding is very much inspired and copied from other sources. I will try to write sources and inspiration.

## Package and upload

First step is to get the normalised lesion masks processed by the `r glossary("NeMo")` tool to get a "dis-`r glossary("connectome")`".

The online instance of the tool offers to freely process lesion masks in batches of 10. You can use the bundled *R*-script to package lesion masks into compressed zip-batches of maximum 10.

1.  Open the `nemo_packing.R` file and edit the variables in the first section, then run the script, from either RStudio or the command terminal window:

    ```{bash}
    #| echo: true
    #| eval: false
    Rscript nemo-packing.R
    ```

1.  Then head over to the [NeMo processing website](https://kuceyeski-wcm-web.s3.us-east-1.amazonaws.com/upload.html) and upload the zip-files, one at a time with your desired settings and atlas for parcellation.

## Glossary

```{r}
glossary_table()
```