# Preparations

```{r}
#| echo: false
source("glossary_setup.R")
```

Following the steps laid out in @sec-start, we got all lesions normalised to standard 1mm MNI space, and they are all located in the individual subject folders, som we just need a few steps to offload work to the NeMo-tool. This was the command used to perform fsl based registration to 1 mm MNI standard space:

    ```{bash}
    #| eval: false 
    #| echo: true           
    sh /codes/folder/00norm_pipeline.sh --do1mm
    ```

1.  Now you should be ready to package for the NeMo tool. The web interface has an upload limit of 10 lesion masks. Open and edit the source-folder in the `nemo-packing.R` script. It will collect all 1mm MNI lesion masks and package in zip-files of max 10 lesion masks each and put them in the provided folder. Save and then run the following:

    ```{bash}
    #| eval: false
    #| echo: true           
    Rscript nemo-packing.R
    ```

Then files were uploaded and sent to the [NeMo tool server]().

## Glossary

```{r}
glossary_table()
```
